quollr: An R Package for Visalizing 2D Models in High Dimensional Space

### 2024-02-22 paper-quollr.Rmd
Change benchmark value to preserve S-curve structure
Since one point was observed at the border in the hexgrid...understood that x_start and y_start shouldn't be always the min values along the axes, need to reduce by some factor which could be able to fit all the bins inside the grid. Therefore reduced by the half of vector/horizontal spacing. Why half? because we don't want to over estimate the x and y start, if a point which is at boudary or the outside the boundary means that it should drag to the grid by the spacing aspects.

Steps:

- First compute hex grid bound values along the x and y axis and generate the all the points within the hex box

- Second for each x-value, find which y values are in the even row

- Then, shift the x values of the even rows

@@

Steps:
- Compute horizontal width of the hexagon

- Compute vertical width of the hexagon and multiply by a factor for overlapping ($sqrt(3) / 2 * 1.15$)

- Obtain hexagon polygon coordinates

- Obtain the number of hexagons in the full grid

- Generate the coordinates for the hexagons

@@

benchmark <- find_benchmark_value(distance_edges = distance, distance_col = "distance")
benchmark
```

>>>>

@@

@@

benchmark <- find_benchmark_value(distance_edges = distance, distance_col = "distance")
benchmark

benchmark <- 0.75
```

### 2024-02-22 paper-quollr.tex
Change benchmark value to preserve S-curve structure
Since one point was observed at the border in the hexgrid...understood that x_start and y_start shouldn't be always the min values along the axes, need to reduce by some factor which could be able to fit all the bins inside the grid. Therefore reduced by the half of vector/horizontal spacing. Why half? because we don't want to over estimate the x and y start, if a point which is at boudary or the outside the boundary means that it should drag to the grid by the spacing aspects.

Steps:

\begin{itemize}
\item
  First compute hex grid bound values along the x and y axis and generate the all the points within the hex box
\item
  Second for each x-value, find which y values are in the even row
\item
  Then, shift the x values of the even rows
\end{itemize}

@@

\begin{verbatim}
#> Rows: 28
#> Columns: 2
#> $ x <dbl> 0.0000000, 0.3464102, 0.6928203, 1.0392305, 0.1732051, 0.5196152, 0.~
#> $ y <dbl> 0.0, 0.0, 0.0, 0.0, 0.3, 0.3, 0.3, 0.3, 0.6, 0.6, 0.6, 0.6, 0.9, 0.9~
\end{verbatim}

@@

Steps:
- Compute horizontal width of the hexagon

\begin{itemize}
\item
  Compute vertical width of the hexagon and multiply by a factor for overlapping (\(sqrt(3) / 2 * 1.15\))
\item
  Obtain hexagon polygon coordinates
\item
  Obtain the number of hexagons in the full grid
\item
  Generate the coordinates for the hexagons
\end{itemize}

@@

\begin{verbatim}
#> Rows: 168
#> Columns: 6
#> $ c_x   <dbl> 0.0000000, 0.0000000, 0.0000000, 0.0000000, 0.0000000, 0.0000000~
#> $ c_y   <dbl> 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0, 0.0,~
#> $ x     <dbl> 0.1732051, 0.1732051, 0.0000000, -0.1732051, -0.1732051, 0.00000~
#> $ y     <dbl> 0.09959292, -0.09959292, -0.19918584, -0.09959292, 0.09959292, 0~
#> $ id    <int> 1, 1, 1, 1, 1, 1, 2, 2, 2, 2, 2, 2, 3, 3, 3, 3, 3, 3, 4, 4, 4, 4~
#> $ hexID <int> 1, 1, 1, 1, 1, 1, 2, 2, 2, 2, 2, 2, 3, 3, 3, 3, 3, 3, 4, 4, 4, 4~
\end{verbatim}

@@

\begin{verbatim}
#>            x   y hexID std_counts
#> 1  0.0000000 0.0     1 0.40000000
#> 2  0.3464102 0.0     2 0.26666667
#> 3  0.1732051 0.3     5 0.86666667
#> 4  0.5196152 0.3     6 0.13333333
#> 5  0.3464102 0.6    10 0.20000000
#> 6  0.6928203 0.6    11 0.53333333
#> 7  0.8660254 0.9    15 0.80000000
#> 8  0.6928203 1.2    19 0.06666667
#> 9  0.5196152 1.5    22 0.06666667
#> 10 0.8660254 1.5    23 1.00000000
#> 11 0.6928203 1.8    27 0.46666667
#> 12 1.0392305 1.8    28 0.20000000
\end{verbatim}

@@

@@

\begin{verbatim}
#> Rows: 75
#> Columns: 4
#> $ pred_UMAP_1 <dbl> 0.1732051, 0.8660254, 0.8660254, 0.0000000, 0.5196152, 0.6~
#> $ pred_UMAP_2 <dbl> 0.3, 0.9, 0.9, 0.0, 0.3, 1.8, 0.9, 0.6, 0.9, 1.8, 0.6, 0.3~
#> $ ID          <int> 1, 2, 3, 4, 6, 7, 8, 9, 11, 12, 14, 15, 16, 17, 19, 20, 21~
#> $ pred_hb_id  <int> 5, 15, 15, 1, 6, 27, 15, 11, 15, 28, 11, 5, 23, 5, 11, 22,~
\end{verbatim}

@@

\begin{verbatim}
#> $mse
#> [1] 0.2612147
#> 
#> $aic
#> [1] -536.7666
\end{verbatim}

>>>>

@@

\begin{verbatim}
#> Rows: 28
#> Columns: 2
#> $ x <dbl> -0.1732051, 0.1732051, 0.5196152, 0.8660254, 0.0000000, 0.3464102, 0~
#> $ y <dbl> -0.15, -0.15, -0.15, -0.15, 0.15, 0.15, 0.15, 0.15, 0.45, 0.45, 0.45~
\end{verbatim}

@@

@@

\begin{verbatim}
#> Rows: 168
#> Columns: 6
#> $ c_x   <dbl> -0.1732051, -0.1732051, -0.1732051, -0.1732051, -0.1732051, -0.1~
#> $ c_y   <dbl> -0.15, -0.15, -0.15, -0.15, -0.15, -0.15, -0.15, -0.15, -0.15, -~
#> $ x     <dbl> 0.0000000, 0.0000000, -0.1732051, -0.3464102, -0.3464102, -0.173~
#> $ y     <dbl> -0.05040708, -0.24959292, -0.34918584, -0.24959292, -0.05040708,~
#> $ id    <int> 1, 1, 1, 1, 1, 1, 2, 2, 2, 2, 2, 2, 3, 3, 3, 3, 3, 3, 4, 4, 4, 4~
#> $ hexID <int> 1, 1, 1, 1, 1, 1, 2, 2, 2, 2, 2, 2, 3, 3, 3, 3, 3, 3, 4, 4, 4, 4~
\end{verbatim}

@@

\begin{verbatim}
#>            x     y hexID std_counts
#> 1  0.1732051 -0.15     2  0.2352941
#> 2  0.0000000  0.15     5  0.5294118
#> 3  0.3464102  0.15     6  0.4117647
#> 4  0.1732051  0.45    10  0.1764706
#> 5  0.5196152  0.45    11  0.3529412
#> 6  0.6928203  0.75    15  0.7058824
#> 7  0.8660254  1.05    20  0.4705882
#> 8  0.6928203  1.35    23  0.2941176
#> 9  1.0392305  1.35    24  0.2352941
#> 10 0.8660254  1.65    28  1.0000000
\end{verbatim}

@@

\begin{verbatim}
benchmark <- 0.75
\end{verbatim}

@@

\begin{verbatim}
#> Rows: 75
#> Columns: 4
#> $ pred_UMAP_1 <dbl> 0.1732051, 0.6928203, 0.8660254, 0.1732051, 0.1732051, 0.8~
#> $ pred_UMAP_2 <dbl> 0.45, 0.75, 1.05, -0.15, 0.45, 1.65, 0.75, 0.75, 0.75, 1.6~
#> $ ID          <int> 1, 2, 3, 4, 6, 7, 8, 9, 11, 12, 14, 15, 16, 17, 19, 20, 21~
#> $ pred_hb_id  <int> 10, 15, 20, 2, 10, 28, 15, 15, 15, 28, 15, 10, 24, 5, 15, ~
\end{verbatim}

@@

\begin{verbatim}
#> $mse
#> [1] 0.3229922
#> 
#> $aic
#> [1] -453.3167
\end{verbatim}
